---
title: 'null'
author: 'null'
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: yes
  github_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = FALSE, message=FALSE, warning=FALSE}
# Packages
library(tidyverse)
library(here)
library(broom)
library(kableExtra)

mytheme <- theme_bw() + theme(panel.grid = element_blank()) + 
  theme(axis.text.x = element_text(size = 15)) +  
  theme(axis.text.y = element_text(size = 15)) +
  theme(axis.title.x = element_text(size = 15)) +
  theme(axis.title.y = element_text(size = 15)) +
  theme(legend.text = element_text(size = 15)) +
  theme(legend.title = element_text(size = 15)) +
  theme(strip.text.x = element_text(size = 15))

# Parameters
  file_data <- here("data/fractions_combined.rds")
  elemental_file_data <- here("data/fractionation_elemental.rds")

#===============================================================================

# read in data
  df <- read_rds(file_data)
  df$litter <- recode(df$litter, n = "No litter", y = "Litter added")
  df$litter <- fct_relevel(df$litter, "No litter", "Litter added")
  df$sampling_point <- recode(df$sampling_point, beginning = "Beginning", end = "End")
  df$water_content <- recode(df$water_content, low = "Low", high = "High")
  df$water_content <- fct_relevel(df$water_content, "low", "high")
  
  df_beg <- df %>% 
  filter(sampling_point == "Beginning")  
  
  df_end <- df %>% 
  filter(sampling_point == "End") 
  
  df_iso <- read_rds(elemental_file_data)
```

## POM fraction amounts

### fPOM amounts
```{r fPOM, echo=FALSE, warnings = FALSE}
fPOM_beg <- df_beg %>% 
ggplot(aes(treatment, fPOM_dry_mg_g, fill = water_content)) + 
  geom_point(shape = 21, size = 2) + 
  facet_grid(water_content ~ litter) + theme_bw() +
  labs(x = "Preincubation treatment", y = "Beginning fPOM amount (mg/g soil)") 
fPOM_beg

fPOM_end <- df_end %>% 
ggplot(aes(treatment, fPOM_dry_mg_g, fill = water_content)) + 
  geom_point(shape = 21, size = 2) + 
  facet_grid(water_content ~ litter) + theme_bw() +
  labs(x = "Preincubation treatment", y = "End fPOM amount (mg/g soil)") 
fPOM_end

fPOm_all <- df %>% 
  ggplot(aes(treatment, fPOM_dry_mg_g, fill = water_content)) + 
  geom_point(shape = 21, size = 2) + 
  facet_grid(water_content ~ litter) + theme_bw() +
  labs(x = "Preincubation treatment", y = "fPOM amount (mg/g soil)") 
fPOm_all

fPOM_change <- df %>% 
  filter(sampling_point != "initial") %>% 
  ggplot(aes(x = water_content, y = fPOM_dry_mg_g, fill = sampling_point)) +
  geom_boxplot(outlier.shape = NA) + 
  labs(fill = "sampling_point") + 
  geom_point(position = position_jitterdodge(jitter.width = 0.025), alpha = 0.3, size = 2) +
  theme_bw(base_size = 16) + 
  ylim(0,50) + 
  labs(x = "Water content", y = "fPOM amount (mg/g soil)", fill = "Sampling time") +
  facet_wrap(.~litter) +
  scale_fill_brewer(palette = "Set1")
fPOM_change + mytheme

fPOM_change_litter <- df %>% 
  filter(sampling_point != "initial" & litter == "Litter added") %>% 
  ggplot(aes(x = water_content, y = fPOM_dry_mg_g, fill = sampling_point)) +
  geom_boxplot(outlier.shape = NA) + 
  geom_point(position = position_jitterdodge(jitter.width = 0.025),
             alpha = 0.3, size = 2) +
  theme_bw(base_size = 16) + 
  ylim(0,50) + 
  labs(x = "Water content", y = "fPOM amount (mg/g soil)", fill = "Sampling time") +
  scale_fill_brewer(palette = "Set1")
fPOM_change_litter + mytheme

m1 <- aov(fPOM_dry_mg_g ~ sampling_point*water_content, data = filter(df, sampling_point != "initial" & litter != "No Litter"))
m1_beg <- aov(fPOM_dry_mg_g ~ water_content*litter, data = df_beg)
m1_end <- aov(fPOM_dry_mg_g ~ water_content*litter, data = df_end)

summary(m1)
tbl_fpom_amount <- 
  tidy(m1, digits = 3) %>% 
  kable(digits = 4)
tbl_fpom_amount
summary(m1_beg)
summary(m1_end)
TukeyHSD(m1)
TukeyHSD(m1_end)
TukeyHSD(m1_beg)
```

Ca treatment does not affect fPOM in any water content/litter treatnebt combination 
fPOM decreases from begininng to end of incubation at high water content 
This result fits delta13C-CO2 data that shows higher delta values at higher water content.
fPOM somewhat increases at low water content - does low water content induce translocation of POM from occluded to free?? Isotope ratio can help identify pathway.

### oPOM amounts 
```{r oPOM, echo=FALSE, warnings = FALSE}
oPOM_beg <- df_beg %>% 
ggplot(aes(treatment, oPOM_dry_mg_g, fill = water_content)) + 
  geom_point(shape = 21, size = 2) + ylim(0,80) +
  facet_grid(water_content ~ litter) + theme_bw() +
  labs(x = "Preincubation treatment", y = "Beginning oPOM amount (mg/g soil)") 
oPOM_beg

oPOM_end <- df_end %>% 
ggplot(aes(treatment, oPOM_dry_mg_g, fill = water_content)) + 
  geom_point(shape = 21, size = 2) + ylim(0,80) + 
  facet_grid(water_content ~ litter) + theme_bw() +
  labs(x = "Preincubation treatment", y = "End oPOM amount (mg/g soil)") 
oPOM_end

oPOM_all <- df %>% 
  ggplot(aes(treatment, oPOM_dry_mg_g, fill = water_content)) + 
  geom_point(shape = 21, size = 2) + ylim(0,50) +
  facet_grid(water_content ~ litter) + theme_bw() +
  labs(x = "Preincubation treatment", y = "oPOM amount (mg/g soil)") 
oPOM_all

oPOM_change <- df %>% 
  filter(sampling_point != "initial") %>% 
  ggplot(aes(x = water_content, y = oPOM_dry_mg_g, fill = sampling_point)) +
  geom_boxplot(outlier.shape = NA) + 
  labs(fill = "sampling_point") + 
  geom_point(position = position_jitterdodge(jitter.width = 0.025), alpha = 0.3, size = 2) +
  theme_bw(base_size = 16) + 
  ylim(0,50) + 
  labs(x = "Water content", y = "oPOM amount (mg/g soil)", fill = "Sampling time") +
  facet_wrap(.~litter) +
  scale_fill_brewer(palette = "Set1")
oPOM_change + mytheme

oPOM_change_litter <- df %>% 
  filter(sampling_point != "initial" & litter == "Litter added") %>% 
  ggplot(aes(x = water_content, y = oPOM_dry_mg_g, fill = sampling_point)) +
  geom_boxplot(outlier.shape = NA) + 
  labs(fill = "sampling_point") + 
  geom_point(position = position_jitterdodge(jitter.width = 0.025), 
             alpha = 0.3, size = 2) +
  theme_bw(base_size = 16) + 
  ylim(0,50) + 
  labs(x = "Water content",
       y = "oPOM amount (mg/g soil)",
       fill = "Sampling time") +
  scale_fill_brewer(palette = "Set1")
oPOM_change_litter + mytheme


m2 <- aov(oPOM_dry_mg_g ~ water_content*sampling_point, data = filter(df, sampling_point != "initial"))
m2_beg <- aov(oPOM_dry_mg_g ~ water_content*litter, data = df_beg)
m2_end <- aov(oPOM_dry_mg_g ~ water_content*litter, data = df_end)

summary(m2)
tbl_opom_amounts <- 
  kable(tidy(m2, digits = 3))
summary(m2_beg)
summary(m2_end)
tbl_opom_amounts
TukeyHSD(m2)
TukeyHSD(m2_end)
TukeyHSD(m2_beg)
```

oPOM decreases from beginning to end in all conditions, especially in low water content when litter is added. Is this translocation to fPOM, or just preferentia decomposition of oPOM vs fPOM in low water content.

### Total POM amounts

```{r total POM, echo=FALSE, warnings = FALSE}
POM_beg <- df_beg %>% 
ggplot(aes(treatment, total_POM, fill = water_content)) + 
  geom_point(shape = 21, size = 2) + ylim(0,80) +
  facet_grid(water_content ~ litter) + theme_bw() +
  labs(x = "Preincubation treatment", y = "Beginning oPOM amount (mg/g soil)") 
POM_beg

POM_end <- df_end %>% 
ggplot(aes(treatment, total_POM, fill = water_content)) + 
  geom_point(shape = 21, size = 2) + ylim(0,80) + 
  facet_grid(water_content ~ litter) + theme_bw() +
  labs(x = "Preincubation treatment", y = "End oPOM amount (mg/g soil)") 
POM_end

POM_all <- df %>% 
  ggplot(aes(treatment, total_POM, fill = water_content)) + 
  geom_point(shape = 21, size = 2) + ylim(0,80) +
  facet_grid(water_content ~ litter) + theme_bw() +
  labs(x = "Preincubation treatment", y = "Total POM amount (mg/g soil)") 
POM_all

POM_change <- df %>% 
  filter(sampling_point != "initial") %>% 
  ggplot(aes(x = water_content, y = total_POM, fill = sampling_point)) +
  geom_boxplot(outlier.shape = NA) + 
  labs(fill = "sampling_point") + 
  geom_point(position = position_jitterdodge(jitter.width = 0.025), alpha = 0.3, size = 2) +
  theme_bw(base_size = 16) + 
  ylim(0,70) + 
  labs(x = "Water content", y = "Total POM amount (mg/g soil)", fill = "Sampling time") +
  facet_wrap(.~litter) + 
  scale_fill_brewer(palette = "Set1")
POM_change + mytheme

m3 <- aov(total_POM ~ sampling_point*water_content, data = filter(df, sampling_point != "initial" & litter != "No Litter"))
m3_beg <- aov(total_POM ~ water_content*litter, data = df_beg)
m3_end <- aov(total_POM ~ water_content*litter, data = df_end)

summary(m3)
summary(m3_beg)
summary(m3_end)
TukeyHSD(m3)
TukeyHSD(m3_end)
TukeyHSD(m3_beg)
```

Total POM (fPOM+oPOM) decrease in amount from beginning to end at high water content, but remain the same at low water content (although changes in each pool). This fits the delta 13C values and indicates POM is sensitive to decomposition at higher water contents. This does not mean C loss, it could mean relative stabilization after microbial processing.

```{r MAOM, echo=FALSE, warnings = FALSE}
SC_beg <- df_beg %>% 
ggplot(aes(treatment, SC_dry_mg_g, fill = water_content)) + 
  geom_point(shape = 21, size = 2) + ylim(800,900) +
  facet_grid(water_content ~ litter) + theme_bw() +
  labs(x = "Preincubation treatment", y = "Beginning SC amount (mg/g soil)") 
SC_beg

SC_end <- df_end %>% 
ggplot(aes(treatment, SC_dry_mg_g, fill = water_content)) + 
  geom_point(shape = 21, size = 2) + ylim(800,900) + 
  facet_grid(water_content ~ litter) + theme_bw() +
  labs(x = "Preincubation treatment", y = "End SC amount (mg/g soil)") 
SC_end

SC_all <- df %>% 
  ggplot(aes(treatment, SC_dry_mg_g, fill = water_content)) + 
  geom_point(shape = 21, size = 2) + ylim(800,900) +
  facet_grid(water_content ~ litter) + theme_bw() +
  labs(x = "Preincubation treatment", y = "SC amount (mg/g soil)") 
SC_all

SC_change <- df %>% 
  filter(sampling_point != "initial") %>% 
  ggplot(aes(x = water_content, y = SC_dry_mg_g, fill = sampling_point)) +
  geom_boxplot(outlier.shape = NA) + 
  labs(fill = "sampling_point") + 
  geom_point(position = position_jitterdodge(jitter.width = 0.025), alpha = 0.3, size = 2) +
  theme_bw(base_size = 16) + 
  ylim(800,900) + 
  labs(x = "Water content", y = "SC amount (mg/g soil)", fill = "Sampling time") +
  facet_wrap(.~litter) +
  scale_fill_brewer(palette = "Set1")
SC_change + mytheme

SC_change_litter <- df %>% 
  filter(sampling_point != "initial" & litter == "Litter added") %>% 
  ggplot(aes(x = water_content, y = SC_dry_mg_g, fill = sampling_point)) +
  geom_boxplot(outlier.shape = NA) + 
  labs(fill = "sampling_point") + 
  geom_point(position = position_jitterdodge(jitter.width = 0.025), 
             alpha = 0.3, size = 2) +
  theme_bw(base_size = 16) + 
  ylim(800,900) + 
  labs(x = "Water content",
       y = "SC amount (mg/g soil)",
       fill = "Sampling time") +
  scale_fill_brewer(palette = "Set1")
SC_change_litter + mytheme


m4 <- aov(SC_dry_mg_g ~ water_content*sampling_point, data = filter(df, sampling_point != "initial"))
m4_beg <- aov(SC_dry_mg_g ~ water_content*litter, data = df_beg)
m4_end <- aov(SC_dry_mg_g ~ water_content*litter, data = df_end)

summary(m4)
summary(m4_beg)
summary(m4_end)

TukeyHSD(m4)
TukeyHSD(m4_end)
TukeyHSD(m4_beg)
```

```{r elemental, echo= FALSE, warnings = FALSE}
ggplot(filter(df_iso, sampling_point == "beginning" & litter == "y"), aes(treatment, delta13C)) + 
  geom_boxplot() + geom_jitter(aes(color = treatment)) +
  facet_grid(fraction ~ water_content, scales = "free") + 
  theme_bw()# + ylim(250,1250)
```

